Gammapy: A Python package for gamma-ray astronomy

### 2022-11-30 src/ms-review.tex
Add astroml andastroquery references

The \iacts data reduction step is done in the same way than described in the 
previous sections but scale up to few thousands of observations. The object
 detection step consists a minima in
finding local maxima in the significance (or TS) maps,  given by the
\code{ExcessMapEstimator} (or \code{TSMapEstimator} respectively).  Further refinements can
include for example  filtering and detection on these maps with techniques from
the "scikit-image" package~\citep{scikit-image}, and outlier detection from
the "scikit-learn" package~\citep{scikit-learn}. This allows e.g., to 
reduce the number of spurious detections at this stage using standard
classification algorithms and then speed up the next step
as less objects will have to be fitted simultaneously. During the modelling
step each object is alternatively fitted with different models in order to
determine their optimal parameters, and the best-candidate model. The
subpackage \code{gammapy.modeling.models} offers a large variety of choice, and the
possibility to add custom models.  Several spatial models (point-source, disk,
Gaussian...), and spectral models (power law, log parabola...) may be tested
for each object, so the complexity of the problem increases rapidly in regions
crowded with multiple extended sources. Finally an object is discarded if its
best-fit model is not significantly preferred over the null hypothesis (no
source) comparing the difference in log likelihood between these two
hypotheses. For the association and classification step, that is tightly
connected to the population studies, we can a minima compare the fitted models
to the set of \gammaray catalogs available in \code{gammapy.catalog}. However
further multi-wavelength cross-matches are usually required to characterize the
sources.

>>>>

The \iacts data reduction step is done in the same way than described in the 
previous sections but scale up to few thousands of observations. The object
 detection step consists a minima in
finding local maxima in the significance (or TS) maps,  given by the
\code{ExcessMapEstimator} (or \code{TSMapEstimator} respectively).  Further refinements can
include for example  filtering and detection on these maps with techniques from
the "scikit-image" package~\citep{scikit-image}, and outlier detection from
the "scikit-learn" package~\citep{scikit-learn}. This allows e.g., to 
reduce the number of spurious detections at this stage using standard
classification algorithms and then speed up the next step
as less objects will have to be fitted simultaneously. During the modelling
step each object is alternatively fitted with different models in order to
determine their optimal parameters, and the best-candidate model. The
subpackage \code{gammapy.modeling.models} offers a large variety of choice, and the
possibility to add custom models.  Several spatial models (point-source, disk,
Gaussian...), and spectral models (power law, log parabola...) may be tested
for each object, so the complexity of the problem increases rapidly in regions
crowded with multiple extended sources. Finally an object is discarded if its
best-fit model is not significantly preferred over the null hypothesis (no
source) comparing the difference in log likelihood between these two
hypotheses.

For the association and classification step, that is tightly connected to the
population studies, we can easily compare the fitted models to the set of
existing \gammaray catalogs available in \code{gammapy.catalog}. Further
multi-wavelength cross-matches are usually required to characterize the
sources. This an e.g. easily be achieved by relying on coordinate
handling from Astropy or affiliated packages such as \textit{AstroML}~\citep{astroML}
or \textit{Astroquery}~\citep{astroquery}.
